\papertitle

### 2021-03-13 source_separation/paper/paper.tex
Last edits

	For example, consider a target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, even though only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. This is the effect we achieve through implementing source separation in computer-assisted orchestration.

@@

	\begin{table}[t]
		\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			& Model & Average distance & Variance\\
			\hline
			\multirow{3}{4em}{Music source separation} & Open-Unmix & 24.48 & \\
			& Demucs & 25.11 & \\
			& TDCN & 26.44 & \\
			\hline
			\multirow{2}{4em}{Universal separation} & NMF & 22.44 & \\
			& TDCN+++ & 24.38 & \\
			\hline
			\multirow{2}{4em}{} & Full target & 24.96 & \\
			\hline
			& Ground truth & 24.19 & \\
			\hline
		\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. ``Full target'' means no separation was performed. Lower values are better.}
		\label{tab:test}
	\end{table}

	\begin{figure}[t]
		\centering
			\includegraphics[width=\columnwidth]{figures/graph.png}
			\caption{Plot showing the average distance and standard deviation between target and solution for each orchestration method.}\label{fig:plot}
	\end{figure}

@@

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. This suggests that methods like NMF can still be useful for specific problems when available data is limited. It is logical that unsupervised methods will perform well for problems in which there is limited data, as they require less data than supervised methods. The NMF also outperformed the ground truth orchestrations, which could be due to the relative simplicity of NMF's output subtargets making subsequent orchestration easier for Orchidea, but more experimentation would need to be done in order to confirm this. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.

>>>>

	For example, consider a target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, even though only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. Although this example is a dynamic orchestration, and we perform only static orchestrations, this paper represents a first step toward achieving dynamic orchestration with source separation.

@@

%	\begin{table}[t]
%		\begin{center}
%		\begin{tabular}{|c|c|c|c|}
%			\hline
%			& Model & Average distance & Variance\\
%			\hline
%			\multirow{3}{4em}{Music source separation} & Open-Unmix & 24.48 & \\
%			& Demucs & 25.11 & \\
%			& TDCN & 26.44 & \\
%			\hline
%			\multirow{2}{4em}{Universal separation} & NMF & 22.44 & \\
%			& TDCN+++ & 24.38 & \\
%			\hline
%			\multirow{2}{4em}{} & Full target & 24.96 & \\
%			\hline
%			& Ground truth & 24.19 & \\
%			\hline
%		\end{tabular}
%		\end{center}
%		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. ``Full target'' means no separation was performed. Lower values are better.}
%		\label{tab:test}
%	\end{table}

%	\begin{figure}[t]
%		\centering
%			\includegraphics[width=\columnwidth]{figures/graph.png}
%			\caption{Plot showing the average distance and standard deviation between target and solution for each orchestration method.}\label{fig:plot}
%	\end{figure}

@@

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. This suggests that methods like NMF can still be useful for specific problems when available data is limited. It is logical that unsupervised methods will perform well for problems in which there is limited data, as they require less data than supervised methods. NMF also outperformed the ground truth orchestrations, which could be due to the relative simplicity of NMF's output subtargets making subsequent orchestration easier for Orchidea, but more experimentation would need to be done in order to confirm this. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.
